\bf Model Visualization Techniques for a Social Network Model

### 2017-04-04 paper.Rnw
add static selection of frames from animation

\noindent%
{\it Keywords:} social network analysis, model visualization \hh{Other keywords?}
\vfill

@@

<<setup, echo = FALSE, message = FALSE, warning = FALSE>>=
options(replace.assign=TRUE,width=70, digits=3)
require(knitr)
opts_chunk$set(fig.path='figure/', cache.path='cache/', fig.align='center', fig.width=5, fig.height=5, par=TRUE, cache=TRUE, concordance=TRUE, autodep=TRUE, message=F, warning=F, echo = FALSE, root.dir = "~/Desktop/Dissertation - LETS GO/SAOM-removing-blindfold/")

library(dplyr)
@

@@

To guide our visual exploration of stochastic actor-oriented models, we used a subset of the 50 actor dataset from the ``Teenage Friends and Lifestyle Study" that is provided on the \texttt{RSiena} webpage. These data come from \citet{friendsdata}, and we chose to only work with a subset of the data to make network visualizations less busy, with changes that are more noticeable. The subset contained actors 20 through 35 and the ties between them, as well as the drinking behavior of each actor at each of the three waves. This specific subset was chosen because it showed somewhat higher connectivity than other subsets, as we've emphasized in the visualizations of the three network adjacency matrices in Figure~\ref{fig:adjmatviz}. For model fitting, we condition on wave 1 and estimate the parameters of the models from the second and third waves. We will also be working with one actor level categorical covariate, drinking behavior. This variable has five values in the original data: (1) does not drink, (2) drinks once or twice a year, (3) drinks once a month, (4) drinks once a week, and (5) drinks more than once a week. The actor covariates adn networks are visualized in Figure~\ref{fig:alldataviz}. 
<<adjmatviz, fig.align='center', fig.cap="A visualization of the adjacency matrices of the three waves of network observations in the ``Teenage Friends and Lifestyle Study'' data. The subset we will be using is outlined in red.", fig.width=8>>=
library(network)
library(sna)
library(geomnet)
source("code/00e_small_friends.R")
view_rs2$wave <- factor(view_rs2$wave)
levels(view_rs2$wave) <- c("Wave 1", "Wave 2", "Wave 3")
ggplot(data= view_rs2, aes(x = x, y=y)) + 
  geom_tile(aes(fill = as.factor(value))) + 
  scale_fill_manual("i likes j", labels=c("no", "yes"), 
                    values = c('white', 'black')) +
  geom_rect(data= NULL, inherit.aes = FALSE, color = 'red',
            aes(xmin = 19.5, xmax = 35.5, ymin = 19.5, ymax = 35.5, fill =NA)) + 
  facet_wrap(~wave) + theme_bw() +
  labs(x = "i", y = "j") + 
  theme(aspect.ratio=1, axis.text = element_blank(), axis.ticks = element_blank()) 
@

@@

The first vizualization we present here is an animation of microsteps simulated to emulate the transition steps from wave 1 to wave 2 the subset of the friends data shown in Figure ~\ref{fig:alldataviz}. Movies similar to our animation were used to visualize the changes of dynamic networks in \citet{dynnetviz}. When each ego node is selected in a microstep, it is emphasized in the animation, then the associated edge either appears or disappears. If there are no changes at a particular microstep, no changes are seen. Some frames of the animations are shown in INSERT STATIC FIGURE OF THE 5-6 DIFFERENT MICROSTEPS AND ONE TRANSITION SET, and the full movie can be viewed at INSERT LINK TO GIF.

<<makinggif>>=
library(RSiena)
library(tidyverse)
library(sna)
library(network)
library(netvizinf)
library(gganimate)
friend.data.w1 <- as.matrix(read.table("../data/s50-network1.dat"))
friend.data.w2 <- as.matrix(read.table("../data/s50-network2.dat"))
friend.data.w3 <- as.matrix(read.table("../data/s50-network3.dat"))
drink <- as.matrix(read.table("../data/s50-alcohol.dat"))
fd2.w1 <- friend.data.w1[20:35,20:35]
fd2.w2 <- friend.data.w2[20:35,20:35]
fd2.w3 <- friend.data.w3[20:35,20:35]
friendshipData <- array(c(fd2.w1, fd2.w2,fd2.w3), dim = c(16, 16, 3))

# running Siena
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
myeffnull <- getEffects(mydata)
myalgorithm <- sienaAlgorithmCreate(projname = 's16_3')
set.seed(823746)
ansnull <- siena07(myalgorithm, data = mydata, effects = myeffnull,
                   returnChains = TRUE, returnDataFrame = TRUE,
                   returnDeps = TRUE, silent = TRUE, verbose = FALSE,
                   batch = TRUE)
ansnullchains <- get_chain_info(ansnull)
ansnullchains %>%
  filter(period == 1) %>%  #only look at chains from wave 1 to wave 2
  group_by(rep) %>%
  select(rep, from = ego, to = alter) %>%
  mutate(val = as.numeric(!from == to),
         from = paste0("V", parse_number(from)+1), # make the chains
         to = paste0("V", parse_number(to)+1)) -> ansnullchainsw1w2
library(geomnet)
colnames(fd2.w1) <- paste0("V", 1:16)
rownames(fd2.w1) <- paste0("V", 1:16)
wave1friends <- fortify(as.adjmat(fd2.w1))
ms1 <- listMicrosteps(dat = wave1friends,
                      microsteps = filter(ansnullchainsw1w2, rep == 1))

XXX HH's code XXX

@@

We also use animation to view the changing structure of the adjacency matrix the microsteps. The adjacency matrices for the three waves of friendship data as shown in Figure~\ref{fig:alldataviz} are ordered by node id. There are 50 nodes in the data, numbered 1-50, and that order is used on the $x$ and $y$ axes for the matrix visualization. Viewing the adjacency matrices with this arbitrary ordering does not provide much information to the viewer about the underlying structure of the network. This lack of perceived structure would be exacerbated in an animation. So, we adjust the ordering so that the viewer can perceive more of the structure of the graph. This process is known as matrix seriation \citep{seriation}.

@@

<<getdata, results='asis'>>=
nulls <- read.csv("data/distribution_null_model.csv")
alt <- read.csv("data/distribution_jumpTT_model.csv")
alt2nd <- read.csv("data/distribution_dblpairs_model.csv")
simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")
means <- simu2 %>% group_by(Model, parameter) %>% summarize(
  means = mean(estimate)
)
library(dplyr)
null_mod_sv <- as.numeric(nulls[,-c(1,6,7)] %>% summarise_each(funs(mean)))
alt_mod_sv <- as.numeric(alt[,-c(1, 7,8)] %>% summarise_each(funs(mean)))
alt_mod2_sv <- as.numeric(alt2nd[,-c(1,7,8)] %>% summarise_each(funs(mean)))
@

@@

<<corplots, fig.cap="A matrix of plots demonstrating the strong correlations between parameter estimate in our SAOMs. The strongest correlation within each model is between $\\beta_1$ and $\\beta_2$.", fig.width=8>>=
library(GGally)
library(tidyr)
simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")

@@

<<averagenet>>=
library(RSiena)
library(tidyverse)
#friend.data.w1 <- as.matrix(read.table("s50_data/s50-network1.dat"))
#friend.data.w2 <- as.matrix(read.table("s50_data/s50-network2.dat"))
#friend.data.w3 <- as.matrix(read.table("s50_data/s50-network3.dat"))
#drink <- as.matrix(read.table("s50_data/s50-alcohol.dat"))
friendshipData <- array(c(fd2.w1, fd2.w2, fd2.w3), dim = c(16, 16, 3))
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
M1eff <- getEffects(mydata)
M2eff <- includeEffects(M1eff, jumpXTransTrip, interaction1 = "alcohol")
M3eff <- includeEffects(M1eff, nbrDist2twice)
library(netvizinf)
data(M1ests_bigfriends)
M1parms <- (means %>% filter(Model == "M1"))$means
M2parms <- (means %>% filter(Model == "M2"))$means
M3parms <- (means %>% filter(Model == "M3"))$means
M1sims1000 <- saom_simulate(dat = mydata, 
                            struct = M1eff,
                       parms = as.numeric(M1parms), 
                       N = 1000)
M2sims1000 <- saom_simulate(dat = mydata, 
                            struct = M2eff,
                       parms = as.numeric(M2parms), 
                       N = 1000)
M3sims1000 <- saom_simulate(dat = mydata, 
                            struct = M3eff,
                       parms = as.numeric(M3parms), 
                       N = 1000)
M1simsdf <- sims_to_df(M1sims1000)
M2simsdf <- sims_to_df(M2sims1000)
M3simsdf <- sims_to_df(M3sims1000)
M1avg <- M1simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M1avgW2 <- M1simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M1avg2 <- M1simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))
M2avg <- M2simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M2avgW2 <- M2simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M2avg2 <- M2simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))
M3avg <- M3simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M3avgW2 <- M3simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M3avg2 <- M3simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))

library(geomnet)
M1avg$from <- paste0("V", M1avg$from)
M1avg$to <- paste0("V", M1avg$to)
M1avg2$from <- paste0("V", M1avg2$from)
M1avg2$to <- paste0("V", M1avg2$to)
M1avgW2$from <- paste0("V", M1avgW2$from)
M1avgW2$to <- paste0("V", M1avgW2$to)
M2avg$from <- paste0("V", M2avg$from)
M2avg$to <- paste0("V", M2avg$to)
M2avgW2$from <- paste0("V", M2avgW2$from)
M2avgW2$to <- paste0("V", M2avgW2$to)
M2avg2$from <- paste0("V", M2avg2$from)
M2avg2$to <- paste0("V", M2avg2$to)
M3avg$from <- paste0("V", M3avg$from)
M3avg$to <- paste0("V", M3avg$to)
M3avgW2$from <- paste0("V", M3avgW2$from)
M3avgW2$to <- paste0("V", M3avgW2$to)
M3avg2$from <- paste0("V", M3avg2$from)
M3avg2$to <- paste0("V", M3avg2$to)

wave2drink <- drink2[,2]
wave2drink <- as.data.frame(wave2drink)
wave2drink$id <- paste0("V", 1:16)
names(wave2drink)[1] <- "drink"
wave3drink <- drink2[,3]
wave3drink <- as.data.frame(wave3drink)
wave3drink$id <- paste0("V", 1:16)
names(wave3drink)[1] <- "drink"
M1avgcov <- merge(M1avg, wave2drink, by.x = "from", by.y = "id", all = T)
M2avgcov <- merge(M2avg, wave2drink, by.x = "from", by.y = "id", all = T)
M3avgcov <- merge(M3avg, wave2drink, by.x = "from", by.y = "id", all = T)
M1avgW2cov <- merge(M1avgW2, wave3drink, by.x = "from", by.y = "id", all = T)
M2avgW2cov <- merge(M2avgW2, wave3drink, by.x = "from", by.y = "id", all = T)
M3avgW2cov <- merge(M3avgW2, wave3drink, by.x = "from", by.y = "id", all = T)
library(tidyr)
M1avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM1
rownames(distmatM1) <- distmatM1$from
distmatM1 <- distmatM1[,-1]
distmatM1 <- as.matrix(sqrt(1/distmatM1))
distmatM1[is.na(distmatM1)] <- 0
M1avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM1W2
rownames(distmatM1W2) <- distmatM1W2$from
distmatM1W2 <- distmatM1W2[,-1]
distmatM1W2 <- as.matrix(sqrt(1/distmatM1W2))
distmatM1W2[is.na(distmatM1W2)] <- 0
M2avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM2
rownames(distmatM2) <- distmatM2$from
distmatM2 <- distmatM2[,-1]
distmatM2 <- as.matrix(sqrt(1/distmatM2))
distmatM2[is.na(distmatM2)] <- 0
M2avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM2W2
rownames(distmatM2W2) <- distmatM2W2$from
distmatM2W2 <- distmatM2W2[,-1]
distmatM2W2 <- as.matrix(sqrt(1/distmatM2W2))
distmatM2W2[is.na(distmatM2W2)] <- 0
M3avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM3
rownames(distmatM3) <- distmatM3$from
distmatM3 <- distmatM3[,-1]
distmatM3 <- as.matrix(sqrt(1/distmatM3))
distmatM3[is.na(distmatM3)] <- 0
M3avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM3W2
rownames(distmatM3W2) <- distmatM3W2$from
distmatM3W2 <- distmatM3W2[,-1]
distmatM3W2 <- as.matrix(sqrt(1/distmatM3W2))
distmatM3W2[is.na(distmatM3W2)] <- 0

library(RColorBrewer)
cols <- brewer.pal(n = 4, "YlOrRd")

>>>>

\noindent%
{\it Keywords:} social network analysis, model visualization, dynamic networks, network visualization, network mapping, animation
\vfill

@@

<<setup, echo = FALSE, message = FALSE, warning = FALSE>>=
options(replace.assign=TRUE,width=70, digits=3)
require(knitr)
opts_chunk$set(fig.path='figure/', cache.path='cache/', fig.align='center', fig.width=5, fig.height=5, par=TRUE, cache=TRUE, concordance=TRUE, autodep=TRUE, message=F, warning=F, echo = FALSE, root.dir = "~/Desktop/Dissertation - LETS GO/SAOM-removing-blindfold/")
@

<<pkgs>>=
library(tidyverse)
library(RSiena)
library(network)
library(sna)
library(geomnet)
library(GGally)
library(netvizinf)
library(RColorBrewer)
library(gridExtra)
library(cowplot)
@

@@

To guide our visual exploration of stochastic actor-oriented models, we used a subset of the 50 actor dataset from the ``Teenage Friends and Lifestyle Study" that is provided on the \texttt{RSiena} webpage. These data come from \citet{friendsdata}, and we chose to only work with a subset of the data to make network visualizations less busy, with changes that are more noticeable. The subset contained actors 20 through 35 and the ties between them, as well as the drinking behavior of each actor at each of the three waves. This specific subset was chosen because it showed somewhat higher connectivity than other subsets, as we've emphasized in the visualizations of the three network adjacency matrices in Figure~\ref{fig:adjmatviz}. For model fitting, we condition on wave 1 and estimate the parameters of the models from the second and third waves. We will also be working with one actor level categorical covariate, drinking behavior. This variable has five values in the original data: (1) does not drink, (2) drinks once or twice a year, (3) drinks once a month, (4) drinks once a week, and (5) drinks more than once a week. The actor covariates adn networks are visualized in Figure~\ref{fig:alldataviz}. 
<<adjmatviz, fig.align='center', fig.cap="A visualization of the adjacency matrices of the three waves of network observations in the ``Teenage Friends and Lifestyle Study'' data. The subset we will be using is outlined in red.", fig.width=8>>=
source("code/00e_small_friends.R")
view_rs2$wave <- factor(view_rs2$wave)
levels(view_rs2$wave) <- c("Wave 1", "Wave 2", "Wave 3")
ggplot(data= view_rs2, aes(x = x, y=y)) + 
  geom_tile(aes(fill = as.factor(value))) + 
  scale_fill_manual("i likes j", labels=c("no", "yes"), 
                    values = c('white', 'black')) +
  geom_rect(data= NULL, inherit.aes = FALSE, color = 'red',
            aes(xmin = 19.5, xmax = 35.5, ymin = 19.5, ymax = 35.5, fill =NA)) + 
  facet_wrap(~wave) + theme_bw() +
  labs(x = "i", y = "j") + 
  theme(aspect.ratio=1, axis.text = element_blank(), axis.ticks = element_blank()) 
@

@@

The first vizualization we present here is an animation of microsteps simulated to emulate the transition steps from wave 1 to wave 2 the subset of the friends data shown in Figure ~\ref{fig:alldataviz}. Movies similar to our animation were used to visualize the changes of dynamic networks in \citet{dynnetviz}. When each ego node is selected in a microstep, it is emphasized in the animation, then the associated edge either appears or disappears. If there are no changes at a particular microstep, no changes are seen. Some frames of the animations are shown in Figure~\ref{fig:makinggif}, and the full movie can be viewed at INSERT LINK TO GIF.

<<makinggif, fig.cap='A selection of images in the microstep animation. The selected edges and nodes are emphasized by changing the size and the color, then when edges are removed, they fade out, shrinking in size, while the nodes change color and shrink to blend in with the other nodes.', fig.width=8>>=
friend.data.w1 <- as.matrix(read.table("data/s50_data/s50-network1.dat"))
friend.data.w2 <- as.matrix(read.table("data/s50_data/s50-network2.dat"))
friend.data.w3 <- as.matrix(read.table("data/s50_data/s50-network3.dat"))
drink <- as.matrix(read.table("data/s50_data/s50-alcohol.dat"))
fd2.w1 <- friend.data.w1[20:35,20:35]
fd2.w2 <- friend.data.w2[20:35,20:35]
fd2.w3 <- friend.data.w3[20:35,20:35]
friendshipData <- array(c(fd2.w1, fd2.w2,fd2.w3), dim = c(16, 16, 3))

# running Siena
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
myeffnull <- getEffects(mydata)
myalgorithm <- sienaAlgorithmCreate(projname = 's16_3')
set.seed(823746)
ansnull <- siena07(myalgorithm, data = mydata, effects = myeffnull,
                   returnChains = TRUE, returnDataFrame = TRUE,
                   returnDeps = TRUE, silent = TRUE, verbose = FALSE,
                   batch = TRUE)
ansnullchains <- get_chain_info(ansnull)
ansnullchains %>%
  filter(period == 1) %>%  #only look at chains from wave 1 to wave 2
  group_by(rep) %>%
  select(rep, from = ego, to = alter) %>%
  mutate(val = as.numeric(!from == to),
         from = paste0("V", parse_number(from)+1), # make the chains
         to = paste0("V", parse_number(to)+1)) -> ansnullchainsw1w2
colnames(fd2.w1) <- paste0("V", 1:16)
rownames(fd2.w1) <- paste0("V", 1:16)
wave1friends <- fortify(as.adjmat(fd2.w1))
ms1 <- listMicrosteps(dat = wave1friends,
                      microsteps = filter(ansnullchainsw1w2, rep == 1))
microsteps <- ms1[1:9]

microsteps_df <- getMicrostepsDF(microsteps)
pte <- pretween_edges(microsteps = microsteps)
ptv <- pretween_vertices(pte = pte, layoutparams = list(n = 16))

# get tweened data for all microsteps
pall <- tween_microsteps(ptv, pte, microsteps_df)

static_pall <- filter(pall, .frame %in% (1:12 * 3-2))

create_net_animate(static_pall) + 
  facet_wrap(~.frame, nrow=3, labeller = 'label_both') + 
  theme(panel.background = element_rect(color = 'black'))
@

@@

We also use animation to view the changing structure of the adjacency matrix the microsteps. The adjacency matrices for the three waves of friendship data as shown in Figure~\ref{fig:alldataviz} are ordered by node id. There are 16 nodes in the data, numbered 1-16, and that order is used on the $x$ and $y$ axes for the matrix visualization. Viewing the adjacency matrices with this arbitrary ordering does not provide much information to the viewer about the underlying structure of the network. This lack of perceived structure would be exacerbated in an animation. So, we adjust the ordering so that the viewer can perceive more of the structure of the graph. This process is known as matrix seriation \citep{seriation}.

@@

<<getdata, results='asis'>>=
nulls <- read.csv("data/distribution_null_model.csv")
alt <- read.csv("data/distribution_jumpTT_model.csv")
alt2nd <- read.csv("data/distribution_dblpairs_model.csv")
simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")
means <- simu2 %>% group_by(Model, parameter) %>% summarize(
  means = mean(estimate)
)
null_mod_sv <- as.numeric(nulls[,-c(1,6,7)] %>% summarise_each(funs(mean)))
alt_mod_sv <- as.numeric(alt[,-c(1, 7,8)] %>% summarise_each(funs(mean)))
alt_mod2_sv <- as.numeric(alt2nd[,-c(1,7,8)] %>% summarise_each(funs(mean)))
@

@@

<<corplots, fig.cap="A matrix of plots demonstrating the strong correlations between parameter estimate in our SAOMs. The strongest correlation within each model is between $\\beta_1$ and $\\beta_2$.", fig.width=8>>=

simu2 <- read.csv("data/simulation-1000-M1-M2-M3.csv")

@@

<<averagenet>>=
#friend.data.w1 <- as.matrix(read.table("s50_data/s50-network1.dat"))
#friend.data.w2 <- as.matrix(read.table("s50_data/s50-network2.dat"))
#friend.data.w3 <- as.matrix(read.table("s50_data/s50-network3.dat"))
#drink <- as.matrix(read.table("s50_data/s50-alcohol.dat"))
friendshipData <- array(c(fd2.w1, fd2.w2, fd2.w3), dim = c(16, 16, 3))
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
M1eff <- getEffects(mydata)
M2eff <- includeEffects(M1eff, jumpXTransTrip, interaction1 = "alcohol")
M3eff <- includeEffects(M1eff, nbrDist2twice)
data(M1ests_bigfriends)
M1parms <- (means %>% filter(Model == "M1"))$means
M2parms <- (means %>% filter(Model == "M2"))$means
M3parms <- (means %>% filter(Model == "M3"))$means
M1sims1000 <- saom_simulate(dat = mydata, 
                            struct = M1eff,
                       parms = as.numeric(M1parms), 
                       N = 1000)
M2sims1000 <- saom_simulate(dat = mydata, 
                            struct = M2eff,
                       parms = as.numeric(M2parms), 
                       N = 1000)
M3sims1000 <- saom_simulate(dat = mydata, 
                            struct = M3eff,
                       parms = as.numeric(M3parms), 
                       N = 1000)
M1simsdf <- sims_to_df(M1sims1000)
M2simsdf <- sims_to_df(M2sims1000)
M3simsdf <- sims_to_df(M3sims1000)
M1avg <- M1simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M1avgW2 <- M1simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M1avg2 <- M1simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))
M2avg <- M2simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M2avgW2 <- M2simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M2avg2 <- M2simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))
M3avg <- M3simsdf %>% filter(!is.na(to) & wave == 1) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M3avgW2 <- M3simsdf %>% filter(!is.na(to) & wave == 2) %>%
  group_by(from, to) %>% 
  summarise(count = n()) %>% 
  mutate(weight = ifelse(from == to, 0, count))
M3avg2 <- M3simsdf %>% filter(!is.na(to)) %>%
 group_by(from, to, wave) %>%
 summarise(count = n()) %>%
 mutate(weight = ifelse(from == to, 0, count))

M1avg$from <- paste0("V", M1avg$from)
M1avg$to <- paste0("V", M1avg$to)
M1avg2$from <- paste0("V", M1avg2$from)
M1avg2$to <- paste0("V", M1avg2$to)
M1avgW2$from <- paste0("V", M1avgW2$from)
M1avgW2$to <- paste0("V", M1avgW2$to)
M2avg$from <- paste0("V", M2avg$from)
M2avg$to <- paste0("V", M2avg$to)
M2avgW2$from <- paste0("V", M2avgW2$from)
M2avgW2$to <- paste0("V", M2avgW2$to)
M2avg2$from <- paste0("V", M2avg2$from)
M2avg2$to <- paste0("V", M2avg2$to)
M3avg$from <- paste0("V", M3avg$from)
M3avg$to <- paste0("V", M3avg$to)
M3avgW2$from <- paste0("V", M3avgW2$from)
M3avgW2$to <- paste0("V", M3avgW2$to)
M3avg2$from <- paste0("V", M3avg2$from)
M3avg2$to <- paste0("V", M3avg2$to)

wave2drink <- drink2[,2]
wave2drink <- as.data.frame(wave2drink)
wave2drink$id <- paste0("V", 1:16)
names(wave2drink)[1] <- "drink"
wave3drink <- drink2[,3]
wave3drink <- as.data.frame(wave3drink)
wave3drink$id <- paste0("V", 1:16)
names(wave3drink)[1] <- "drink"
M1avgcov <- merge(M1avg, wave2drink, by.x = "from", by.y = "id", all = T)
M2avgcov <- merge(M2avg, wave2drink, by.x = "from", by.y = "id", all = T)
M3avgcov <- merge(M3avg, wave2drink, by.x = "from", by.y = "id", all = T)
M1avgW2cov <- merge(M1avgW2, wave3drink, by.x = "from", by.y = "id", all = T)
M2avgW2cov <- merge(M2avgW2, wave3drink, by.x = "from", by.y = "id", all = T)
M3avgW2cov <- merge(M3avgW2, wave3drink, by.x = "from", by.y = "id", all = T)

M1avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM1
rownames(distmatM1) <- distmatM1$from
distmatM1 <- distmatM1[,-1]
distmatM1 <- as.matrix(sqrt(1/distmatM1))
distmatM1[is.na(distmatM1)] <- 0
M1avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM1W2
rownames(distmatM1W2) <- distmatM1W2$from
distmatM1W2 <- distmatM1W2[,-1]
distmatM1W2 <- as.matrix(sqrt(1/distmatM1W2))
distmatM1W2[is.na(distmatM1W2)] <- 0
M2avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM2
rownames(distmatM2) <- distmatM2$from
distmatM2 <- distmatM2[,-1]
distmatM2 <- as.matrix(sqrt(1/distmatM2))
distmatM2[is.na(distmatM2)] <- 0
M2avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM2W2
rownames(distmatM2W2) <- distmatM2W2$from
distmatM2W2 <- distmatM2W2[,-1]
distmatM2W2 <- as.matrix(sqrt(1/distmatM2W2))
distmatM2W2[is.na(distmatM2W2)] <- 0
M3avg[,-3] %>% spread(to, weight) %>% data.frame-> distmatM3
rownames(distmatM3) <- distmatM3$from
distmatM3 <- distmatM3[,-1]
distmatM3 <- as.matrix(sqrt(1/distmatM3))
distmatM3[is.na(distmatM3)] <- 0
M3avgW2[,-3] %>% spread(to, weight) %>% data.frame-> distmatM3W2
rownames(distmatM3W2) <- distmatM3W2$from
distmatM3W2 <- distmatM3W2[,-1]
distmatM3W2 <- as.matrix(sqrt(1/distmatM3W2))
distmatM3W2[is.na(distmatM3W2)] <- 0

cols <- brewer.pal(n = 4, "YlOrRd")

plotM1W2 <- ggplot(data = M1avgcov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/251, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM1)
           ) + 
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  #labs(title = "Wave 2, M1") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm")) + 
  labs(title = "Model 1 Simulated Wave 2")
plotM1W3 <- ggplot(data = M1avgW2cov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/388.5, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM1W2)
           ) + 
  scale_color_manual(values = cols[2:4], name = "Drinking\nBehavior") + 
  #labs(title = "Wave 3, M1") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
plotM2W2 <- ggplot(data = M2avgcov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/325, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM2)
           ) + 
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  #labs(title = "Wave 2, M2") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm")) + 
  labs(title = "Model 2 Simulated Wave 2")
plotM2W3 <- ggplot(data = M2avgW2cov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/357, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM2W2)
           ) + 
  scale_color_manual(values = cols[2:4], name = "Drinking\nBehavior") + 
  #labs(title = "Wave 3, M2") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
plotM3W2 <- ggplot(data = M3avgcov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/258, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM3)
           ) + 
  scale_color_brewer(palette = "YlOrRd", name = "Drinking\nBehavior") + 
  #labs(title = "Wave 2, M3") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm")) + 
  labs(title = "Model 3 Simulated Wave 2")
plotM3W3 <- ggplot(data = M3avgW2cov) + 
  geom_net(aes(from_id = from, to_id = to, linewidth = weight/372.5, color = as.factor(drink)), 
           arrowgap = .03, size = 3,arrowsize = .5,
           directed = TRUE, curvature = .2,
           #layout.alg = "fruchtermanreingold"
           layout.alg = "kamadakawai",
           layout.par = list(elen = distmatM3W2)
           ) + 
  scale_color_manual(values = cols[2:4], name = "Drinking\nBehavior") + 
  #labs(title = "Wave 3, M3") + 
  scale_size_continuous(name = "Weight") + 
  theme_net() + 
  theme(plot.title = element_text(hjust = .5), legend.position = 'none',plot.margin=unit(c(0,0,0,0),"mm"))
